---
title: "The Power of Rumor Mill: How Rumors Shape Political Decision Making"
short: "Replication of Berinsky (2017)"
journal: "AER" # AER, AEJ, PP, JEL
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
vol: 1
issue: 1
jel:
  - A10
  - A11
keywords:
  - Rumors
  - Political decision making
author:
  - name: Dan Xu
    firstname: Dan
    surname: Xu
    email: zedan.xu@mail.utoronto.ca
    affiliation: University of Toronto
acknowledgements: |
  Acknowledgements
abstract: |
  This project is a replication of Berinsky's study of political rumors surrounding the 2010 U.S. health care reform act. I re-examined the structure of the experimental design and re-analyzed the results generated by the survey experiment.
output: rticles::aea_article
---
```{r,message=FALSE, warning=FALSE,echo = F, results = 'hide'}
library(tidyverse)
library(haven)
# rm(list = ls())
```

```{r, echo = F, eval = F}
SSI <- 
  haven::read_dta("/Users/dans/Documents/Berinsky_2017/dataset/SSI Wave 1 & 2 combined.dta") 
```

```{r echo = F,eval = F}
SSI_df <- 
  SSI %>% 
  select(- caseid) %>% 
  as_tibble()
head(SSI_df)
```

```{r save datasets,eval = F,echo = F}
# Save multiple objects
save(SSI_df, file = "data.RData")
```

```{r load data,message=FALSE, warning=FALSE,echo = F,  results = 'hide'}
# To load the data again
load("data.RData")
```

\section{Experimental design}

Berinsky conducted the survey experimental using a two wave online survey. From 17 - 19 May 2010, Berinsky  performed a between subjects design experiment, in which the outcome is only measured post - treatment, online with a national sample of 1701 American adults. The second wave was administered to only 699 of the initial respondents from 25 - 29 May 2010. The experiment was conducted by Survey Sample International (SSI) - a U.S. based digital research business that offers survey sampling and related services for market survey research. The survey was constructed according to the the US adult population on education, gender, age, geography, and income.    

\subsection{Between vs. Within Subject Design}

Widely used in Psychological studies, between-subject experimental designs are an experimental approach in which each subject is tested under one condition and only exposed to a single treatment. In Berinsky's experimental design, the survey respondents were randomly assigned to four different treatment groups and one control group and presented with the stories regarding the controversial 2010 ACA. The following table details the conditions which the survey respondents received, 

\begin{table}
\caption{The experimental treatments and control of the study}

\begin{tabular}{lll}
& Condition & Description \\
1 & Rumor & Rumor \\
2 & Rumor and Correction & Rumor and correction \\
3 & Rumor and Republican correction & Rumor and correction, Quote from Republican senator \\
4 & Rumor and Democratic correction & Rumor and correction, quote from emocratic representative \\
5 & Control & No experimeital conditions
\end{tabular}
\begin{tablenotes}
Table provides a brief description of the experimental design. See text for details.
\end{tablenotes}
\begin{tablenotes}[Source]
Table drawn on the original Berinsky(2017) article.
\end{tablenotes}
\end{table}



different people test each condition, so that each person is only exposed to a single user interface.

Within-subjects (or repeated-measures) study design: the same person tests all the conditions (i.e., all the user interfaces).



Summary
to examine the impact of the partisan identity of the provider of the rumor correction, Berinsky ran a between - subjects design experiment on 
In May 2010, two months after the passage of the ACA, I ran a between-subjects design experiment on an internet panel to test the efficacy of various corrective strategi

\subsection{Treat and control conditiions} 
How many respondents were assignmend to the treatment and control groups? 
Respondents were randomly assigned to one of five conditions (the four experimental treatments and the control)


}

Sample figure:

\begin{figure}
Figure here.

\caption{Caption for figure below.}
\begin{figurenotes}
Figure notes without optional leadin.
\end{figurenotes}
\begin{figurenotes}[Source]
Figure notes with optional leadin (Source, in this case).
\end{figurenotes}
\end{figure}

Sample table:

\begin{table}
\caption{Caption for table above.}

\begin{tabular}{lll}
& Heading 1 & Heading 2 \\
Row 1 & 1 & Rumor in the form of quotes endorsed by opponents \\
Row 2 & 3 & 4%
\end{tabular}
\begin{tablenotes}
Table notes environment without optional leadin.
\end{tablenotes}
\begin{tablenotes}[Source]
Table notes environment with optional leadin (Source, in this case).
\end{tablenotes}
\end{table}

References here (manual or bibTeX). If you are using bibTeX, add your bib file
name in place of BibFile in the bibliography command.
% Remove or comment out the next two lines if you are not using bibtex.
\bibliographystyle{aea}
\bibliography{references}

% The appendix command is issued once, prior to all appendices, if any.
\appendix

\section{Mathematical Appendix}
